Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-05-28 tse19/main.tex
update section 2 and 3

\IEEEtitleabstractindextext{%
\begin{abstract}
Dealing with high costs of testing remains an important problem in
Software Engineering.  Test suite parallelization is an important
approach to address this problem. \Mar{Sotero, vc. atualizou estas
  macros?}  Considering a set of \numSubjs{} Java projects we analyzed
from \github\, we found that \percentMedLongRunning{} of the them
contain long-running test suites, but parallelization features still
seem underutilized in practice~---~only \percentParallelUpdated{} of
projects with long-running test suites parallelize test
execution. According to a survey we conducted, the main reason for
adoption resistance was the concern to deal with concurrency issues
that could result in test flakiness.
%% This Results suggest that, on
%% average, developers prefer high predictability than high performance
%% in running tests.

@@

\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
adoption.  First, we measured usage of parallelism in open-source projects.
Then, we ran a survey with developers to understand the reasons that could
explain resistance to using the technology.\Comment{ For the quantitative
analysis we checked both statically (parsing build files) and dynamically
(monitoring execution of build files) for the presence of parallelization.}
Considering only the projects whose test suites take longer than a minute to
run, we found that only \percentParallelUpdated{} of them use parallelism.  We
also contacted developers from a selection of costly projects that did not use
parallelization to understand the reasons for not using parallelization.
Dealing with concurrency-related issues (\eg{}, the extra work to organize test
suite to avoid concurrency errors) and the availability of continuous
integration services were the most frequently answered reasons for not
considering parallelization.

\noindent\emph{Speedups.}~We used two setups to measure speedups.  In one setup
we measured speedups obtained on projects that run test suites in parallel by
default.  In the other setup, we evaluated how execution scales with the number
of available cores in the machine.\Comment{We did not change parallel
configurations on that setup.  For comparison, we disabled parallel execution to
obtain the running time of a sequential execution.}  Considering the first
setup, results indicate that the average speedup of parallelization was
\avgSpeedup{}x.  Although we found cases with very high speedups (\eg{}, 28.8x
for project Jcabi), we also found cases where the speedups were not very
significant.  Considering the scalability experiment, we noticed, perhaps as
expected, that parallelization obtained with forking JVMs scales with the number
of cores but the speedups are bounded by long-running test classes.

@@

\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
fragment of a Maven configuration file, known as \pomf{}, highlighting
options to run tests using the parallel execution mode \ForkParMeth{}.
Maven implements this feature through its Surefire JUnit test
plugin~\cite{maven-surefire-plugin}.  With this configuration, Maven
forks one JVM per core (\CodeIn{forkCount} parameter) and uses five
threads (\CodeIn{threadCount} parameter) to run test methods
(\CodeIn{parallel} parameter) within each forked JVM. In addition, Maven reuses
created JVMs on subsequent forks when execution of a test class
terminates (\CodeIn{reuseFork} parameter). This is an example of a
very aggressive setup, \ie{}, a setup that could substantially speedup
execution but could introduce test flakiness if test code is not
prepared for parallel execution.

@@

\Mar{Sotero, por favor, verifique que os numeros que estao aparecendo
  no texto (usados nas macros) estao corretos! Vc. nao precisa
  atualizar o ingles, mas se os dados nao estiverem corretos e vc. nao
  explicar as mudanca (em portugues mesmo) nao vamos ter condicoes de
  revisar.}

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria:\Mar{alguma restricao
  sobre o numero minimo de testes por projeto?$\rightarrow$} (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}\Mar{ver comentario abaixo}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that one hundred stars was enough to eliminate trivial subjects. The
third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
(\eg{}, \emph{pom.xml}) in the directory structure. 
\textcolor{red}{[S.J: Hoje em dia ja e possivel buscar projeto que
    contenha determinado arquivo pelo Github API (ex.: pom.xml),
    SearchCode, foi utilizado PyGithub para filtrar os projetos
]}\Mar{Sotero, vc. usou ou nao usou este recurso da API do GitHub? Estou muito cofuso
  aqui (por isto tive que interromper revisao). Se vc usou, este
  quarto criterio precisa sair e entrar outro dizendo
  explicitamente que usamos isto. Fora isto, logo abaixo vc. diz que
  de um total de 4111, 3154 *nao* eram Maven. Mas, como eh possivel,
  se vc. garante (atraves deste recurso) a presenca de um arquivo pom.xml?}

@@

We used the following methodology to select projects for analysis. After obtaining the list of potential projects from GitHub, we
filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and non-deterministic results observed from sequential
executions.
As of August 25th 2017, our search criteria returned a total of
\SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management
system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects. 
 \textcolor{red}{[S.J: Utilizando o script desse experimento, Foram encontrado um total de 4111, onde 3154 nao eram Maven e 957 eram Maven. Dos 3154 que nao eram Maven, 2302 eram Gradle (73\%) ]}

@@

\begin{figure}[ht]
  \vspace{-5mm}
  \centering
  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} with missing dependencies,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.\Mar{Sotero, este plot e
    macros estao atualizados?}}
\end{figure}

@@

\Mar{Por que isto esta em uma secao ``Objects of Analysis''? Eh esta
  mesmo a configuracao de maquina que vc. usou.}
To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor
machine with eight virtual CPUs (four cores with two native threads each) and
16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).  We
used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
suites. To process test results and generate plots we used Python\Comment{ 3.4},
Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
replication on our website~\cite{ourwebpage}.  This includes supporting
scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
data)} and the full list of projects.

>>>>

\IEEEtitleabstractindextext{%
\begin{abstract}
Dealing with high costs of testing remains an important problem in
Software Engineering.  Test suite parallelization is an important
approach to address this problem. \Mar{Sotero, vc. atualizou estas
  macros?} \textcolor{red}{[S.J: atualizado.]} Considering a set of \numSubjs{} Java projects we analyzed
from \github\, we found that \percentMedLongRunning{} of the them
contain long-running test suites, but parallelization features still
seem underutilized in practice~---~only \percentParallelUpdated{} of
projects with long-running test suites parallelize test
execution. According to a survey we conducted, the main reason for
adoption resistance was the concern to deal with concurrency issues
that could result in test flakiness.
%% This Results suggest that, on
%% average, developers prefer high predictability than high performance
%% in running tests.

@@

\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
adoption.  First, we measured usage of parallelism in open-source projects.
Then, we ran a survey with developers to understand the reasons that could
explain resistance to using the technology.\Comment{ For the quantitative
analysis we checked both statically (parsing build files) and dynamically
(monitoring execution of build files) for the presence of parallelization.}
Considering only the projects whose test suites take longer than a minute to
run, we found that only \percentParallelUpdated{} of them use parallelism.  We
also contacted developers from a selection of costly projects that did not use
parallelization to understand the reasons for not using parallelization.\textcolor{red}{[S.J: nao fizemos isso.]}
Dealing with concurrency-related issues (\eg{}, the extra work to organize test
suite to avoid concurrency errors) and the availability of continuous
integration services were the most frequently answered reasons for not
considering parallelization.

\noindent\emph{Speedups.}~We used two setups to measure speedups.  In one setup
we measured speedups obtained on projects that run test suites in parallel by
default.  In the other setup, we evaluated how execution scales with the number
of available cores in the machine.\Comment{We did not change parallel
configurations on that setup.  For comparison, we disabled parallel execution to
obtain the running time of a sequential execution.}  Considering the first
setup, results indicate that the average speedup of parallelization was
\avgSpeedup{}x.  Although we found cases with very high speedups (\eg{}, 5.77x
for project Twilio Java), we also found cases where the speedups were not very
significant.  Considering the scalability experiment, we noticed, perhaps as
expected, that parallelization obtained with forking JVMs scales with the number
of cores but the speedups are bounded by long-running test classes.

@@

\noindent\emph{Example:} Figure~\ref{fig:surefire} shows a
fragment of a Maven configuration file, known as \pomf{}, highlighting
options to run tests using the parallel execution mode \ForkParMeth{}.
Maven implements this feature through its Surefire JUnit test
plugin~\cite{maven-surefire-plugin}.  With this configuration, Maven
forks one JVM per core (\CodeIn{forkCount} parameter) and uses five
threads (\CodeIn{threadCount} parameter) to run test methods
(\CodeIn{parallel} parameter) within each forked JVM. In addition, Maven reuses
created JVMs on subsequent forks when execution of a test class
terminates (\CodeIn{reuseFork} parameter). This is an example of a
very aggressive setup, \ie{}, a setup that could substantially speedup
execution but could introduce test flakiness if test code is not
prepared for parallel execution.

@@

\Mar{Sotero, por favor, verifique que os numeros que estao aparecendo
  no texto (usados nas macros) estao corretos! Vc. nao precisa
  atualizar o ingles, mas se os dados nao estiverem corretos e vc. nao
  explicar as mudanca (em portugues mesmo) nao vamos ter condicoes de
  revisar.}
\textcolor{red}{[S.J: Ok.]}
We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria:\Mar{alguma restricao
  sobre o numero minimo de testes por projeto?$\rightarrow$}  \textcolor{red}{[S.J: Nao, mantemos as mesmas restricoes por ordem descendentes das stars]} (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}\Mar{ver comentario abaixo}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that one hundred stars was enough to eliminate trivial subjects. The
third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
(\eg{}, \emph{pom.xml}) in the directory structure. 
\Mar{Sotero, vc. usou ou nao usou este recurso da API do GitHub? Estou muito cofuso
  aqui (por isto tive que interromper revisao). Se vc usou, este
  quarto criterio precisa sair e entrar outro dizendo
  explicitamente que usamos isto. Fora isto, logo abaixo vc. diz que
  de um total de 4111, 3154 *nao* eram Maven. Mas, como eh possivel,
  se vc. garante (atraves deste recurso) a presenca de um arquivo pom.xml?}

\textcolor{red}{[S.J: Tivemos dois momentos, o primeiro momento, usamos os mesmos criterios e script do paper ase17 para minerar os subjects. No segundo momento, usamos uma library python chamado PyGithub, ``https://github.com/PyGithub/PyGithub``, para gerenciar recursos do Github API. Utilizamos a funcao search\_code, que busca por especifico arquivo em repositorios ``pygithub.search\_code(pom in:pom.xml filename:pom.xml,order=desc)``, curl Github API ``https://api.github.com/search/code?q=pom in:pom.xml+filename:pom.xml``, e em seguida filtramos esses subjects com os crietrios (2) e (3) do paper.    
]}

@@

We used the following methodology to select projects for analysis. After obtaining the list of potential projects from GitHub, we
filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and non-deterministic results observed from sequential
executions.
As of March 5th 2019, our search criteria returned a total of
\SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management
system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects. 
 \textcolor{red}{[S.J: Foi possivel observar que houve uma consideravel conversao de ferramenta de automacao, do Maven para Gradle,  dos 3154 subject que nao eram Maven, 2302 eram Gralde (73\%). Projeto como o MapDB, que e bastante citado no paper de ase17, atualmente converteu-se a Gradle. ]}

@@

\begin{figure}[ht]
  \vspace{-5mm}
  \centering
  \includegraphics[width=0.37\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} with missing dependencies,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.\Mar{Sotero, este plot e
    macros estao atualizados?}} \textcolor{red}{[S.J:Atualizado.]}
\end{figure}

@@

\Mar{Por que isto esta em uma secao ``Objects of Analysis''? Eh esta
  mesmo a configuracao de maquina que vc. usou.} \textcolor{red}{[S.J:Atualizado.]}
To run our experiments, we used a Intel Xeon ES-2650 v4 (2.20 GHz)
with eight virtual CPUs (four cores with two native threads each) and
16GB of memory, running Ubuntu 18.10 Cosmic Cuttlefish (64-bit version).  We
used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
suites. To process test results and generate plots we used Python\Comment{ 3.4},
Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
replication on our website~\cite{ourwebpage}.  This includes supporting
scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
data)} and the full list of projects.
